---
title: "COVID-19 trend analysis Belgium"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
    source_code: "https://github.com/pjvolders/Covid19TrendAnalysis"
twitter:
  site: "@rstudio"
  creator: "@pjvolders"
---

```{r setup, include=FALSE}
library(flexdashboard)
setwd("../")
source("ConfirmedCasesPlot.R")
library(plotly)


```

Home {data-icon="fa-home"}
===================================== 

Row
-------------------------------------
    
### Growth in number of deaths compared to other countries
    
```{r}
ggplotly(pdelaylog)
```
    
### Number of patients in intensive care wards

```{r}
ggplotly(be_icu) %>% style(textposition = "right")
```

Row
-------------------------------------
    
### Cummulative number of confirmed COVID-19 cases
    
```{r}
ggplotly(plin)
```

Trends {data-icon="fa-chart-line"}
===================================== 

Row
-------------------------------------
    
### Trend in daily increase in reported cases
    
```{r}
ggplotly(increase_conf)
```
    
### Trend in number of patients admitted to an intensive care ward in Belgium

```{r}
ggplotly(nr_increase_icu)
```

About {.sidebar}
===================================== 

## Infomation

Worldwide data obtained from the Johns Hopkins University Center for Systems Science and Engineering (JHU CSSE) [GitHub repository](https://github.com/CSSEGISandData/COVID-19).

Belgium data is obtained from the Sciensano [EPISTAT](https://epistat.wiv-isp.be/covid/) platform

Latest update: ``r Sys.time()``

[@pjvolders](https://twitter.com/pjvolders)



